The Astropy Project: xx

### 2021-12-01 src/ms.tex
some rough words in the intro

Over the last decade, \python has grown enormously in popularity and has become
a dominant programming language in the astronomical community.

>>>>

Over the last decade, \python has grown enormously in popularity to become a
dominant programming language in the astronomical (and broader) scientific
community.
For example, Figure~\ref{fig:python-mentions} shows the number of yearly
full-text mentions of \python as compared to a few other programming languages
in refereed articles in the astronomical literature, demonstrating its nearly
exponential growth in popularity.
The rapid adoption of \python by astronomy researchers, students, observatories,
and technical staff combined with an associated increase in awareness and
interest about open-source software tools is leading a paradigm shift in the way
research is done, data is analyzed, and results are shared.

TODO:  https://physicsworld.com/a/standing-on-the-shoulders-of-programmers/

A major reason that Python has been adopted in the sciences is the huge amount
of community-oriented, open-source software tools that are available to
anyone...TODO.
TODO: Numpy, scipy, matplotlib, scientific software ecosystem.
In astronomy, one of the first large, community-oriented, open-source \python packages ... was Astropy ... (note: yt)
TODO: words about astropy core package.
TODO: The core package is now largely stable and provides core foundational tools.
TODO: Astropy has expanded to become the Astropy Project: Broader scope than core package. Core package, Ecosystem of tools, Community of users, developers, maintainers

Transition of needs: From new features, to community development, sustainability, ...
- pipeline between User, Participant, Code contributor, Maintainer, Coordinator.

Funding received:
- Moore
- NASA
